Towards Detecting Stalkerware Through Network Traces

### 2019-03-19 paper/main.tex
edit traffic result

>>>>

\begin{table*}
\begin{tabular}{p{5cm}p{5cm}p{5cm}}
	\toprule
	Generalized Signature & Unique Apps & Total Apps \\
	Domain contains “spy,” “track,” “find” & 6 & 12 \\
	SNI contains “spy,” “track,” “find” & 6 & 6 \\
	User-Agent contains “spy,” “track,” “find” & 1 & 3 \\
	User-Agent contains known app name & 1 & 1 \\
	Domain contains known app name & 3 & 4 \\
	SNI contains known app name & 1 & 1 \\
	SNI contains known app manufacturer & 3 & 3 \\
	Domain contains known app manufacturer & 3 & 3 \\
	\midrule
\end{tabular}
\end{table*}

\section{Reskinned Applications}
